
%%%%%%%%% BIOGRAPHICAL SKETCH -- 2 pages

\required{Curriculum Vitae: Bryan James Lunt}
% Your Bio should be divided into the following sections
% (a) Professional Preparation (education):
% Undergrad, Major, Year
% Graduate, Major, Year
% Postdoc, Area, Years-Inclusive
% (b) Appointments:  most recent first.
% (c) Publications:  5 related to the proposal, and 5 "Other Significant Publications"
% (d) Synergistic Activities (math-enhancing activities that were not
% part of your main job description, like editorial boards and
% conference organizing - any Math-related volunteer work.
% these are often similar to Broader Impacts
%
% (e) Collaborators & Other Affiliations: (use the following sections)
% list in alphabetical order, and include current affiliations parenthetically
% Collaborators and Co-editors: past 48 months.  If none, write "none"

\section*{General Information}
\begin{tabular}{l l}
Name: & Bryan James Lunt \\
Current Affiliation: & Department of Computer Science, University of Illinois at Urbana-Champaign \\
 &	201 N Goodwin Ave, Urbana, IL 61801 \\
Institution E-Mail: & bjlunt2@illinois.edu \\
Alternate E-Mail: & bryan.j.lunt@gmail.com \\
GitHub: & https://github.com/bryan-lunt/ \\

\end{tabular}


\nocite{Morcos2011a,Procaccini2011a,Lunt2010a}
\nocite{LUNT201017,Lunt393835}
\section*{Professional Preparation}
\begin{tabular}{l c r}

UIUC & {\bf Computer Science Graduate education} & Aig. 2014 - present {\it (PhD. in progress)}\\
UC, San Diego & {\bf Computer Science Graduate education} & Sep. 2011 - July 2014 {\it (transferred)}\\
CSU, Chico & {\bf Continued Education: Physics and CS} & Jan. - May 2011\\
CSU, Chico & {\bf B.S. Computer Science}  & {\it Graduated} May 2008\\
\end{tabular}

\section*{Other Qualifications}
$1^{st}$ dan, Musoshinden-ryu (Yokohama variant), All Japan Iaido Federation, Tokyo, Nov. 22, 2020\\

\section*{Human Languages}
\begin{tabular}{l l}

{\bf English}: & Native \\
{\bf Japanese}: & Fluent (Translation samples available upon request.) \\

\end{tabular}

\section*{Selected Appointments}
\begin{itemize}
	\item {\bf Research Assistant}; Department of Computer Science; UIUC; Aug. 2014-{\it (ongoing) }
		\subitem Supervisor: {\bf Professor Saurabh Sinha}
		\subitem Wrote \cite{Lunt393835} and contributed to \cite{Tabe-Bordbar2020.11.08.373555,Khajouei2020.02.07.939264} . Maintained and contributed heavily to GEMSTAT code.
		
	\item {\bf Teaching Assistant}; Computer Science and Engineering; UC San Diego; Sep.-Dec. 2012
		\subitem Supervisor: {\bf Professor Charles Elkan }
		\subitem Assistant for {\it CSE 250A: Probabilistic Reasoning and Learning}: Grading quizzes and homeworks, holding office hours, leading review sections.
		
	\item {\bf Research Assistant}; Computer Science and Engineering; UC San Diego; Mar. 2012 - ?
		\subitem Supervisor: {\bf Professor Charles Elkan }
		\subitem Researching improvements into the method of \cite{MorcosE1293,10.1371/journal.pone.0019729} and synergistic combinations of those methods with methods from Machine Learning.
	
	\item {\bf Research Assistant}; Center for Theoretical Biological Physics; UC San Diego; Dec. 2009 - Oct. 2010
		\subitem Supervisor: {\bf Professor Terence Hwa }
		\subitem Used methods developed below to investigate the bacterial Tryptophan biosynthesis pathway, and predict multimerization interfaces for eukaryotic cytoskeletal proteins. Created webservice versions of all major tools for covariance analysis. Contributed heavily to \cite{MorcosE1293,10.1371/journal.pone.0019729}.
	
	\item {\bf Visiting Scientist}; Max Planck Institute for Molecular Genetics; Berlin, Germany; Sep - Nov. 2009
		\subitem Supervisor: {\bf Group Leader Peter Arndt }
		\subitem Investigated the dynamics of ancestor reconstruction under various phylogenetic and mutational models.
	
	\item {\bf Research Assistant}; Institute for Scientific Interchange Foundation; Torino, Italy; Jan. - July 2009
		\subitem Supervisor: {\bf Professor Martin Weigt }
		\subitem Continued development of tools for Protein-Protein interaction prediction. Developing standardized user-friendly dataset generation tools. Published \cite{LUNT201017}, and contributed to \cite{pmid24603210}.
	
	\item {\bf Research Assistant}; Center for Theoretical Biological Physics; UC San Diego; June - Dec. 2008
		\subitem Supervisor: {\bf Professor Terence Hwa }
		\subitem Developed software and databases for Protein-Protein interaction prediction using information theoretic methods, and tools for creating nightly sequence alignments based on latest available genome data. Performed systems administrative tasks.
		
	\item {\bf Japanese-English Translator / Software Developer}; Musketeer Information Research; Chico, CA / Yokohama, Japan; Feb. 2006 - May. 2008
		\subitem Supervisor: {\bf Self / Client }
		\subitem Developed mission-critical applications, set IT policy, provided remote and on-site disaster-response. Rapidly prototyped software to support newly developing products and workflows in an environment of constantly changing requirements. Carefully interviewed client staff to educe requirements. Summarised and translated Japanese financial news articles, identifying and focusing on points interesting to the client, points likely to draw reader attention, and important figures. Created coherent summaries that flow smoothly.

\end{itemize}

\section*{Publications}
\nocite{LUNT201017,Lunt393835}
\nocite{Tabe-Bordbar2020.11.08.373555,canby-etal-2020-university,Khajouei2020.02.07.939264}
\nocite{pmid24603210,MorcosE1293,10.1371/journal.pone.0019729}
\renewcommand{\refname}{\vspace*{-1cm}}
\bibliography{GoogleScholar_Pubs.bib}

%\section*{Collaborators and Other Affiliations}
%\input{BryansCollaborators.tex}
%\subsection*{M.S. Thesis Advisor: Professor Charles Elkan}
%Department of Computer Science and Engineering; University of California, San Diego
%\subsection*{Professional Affiliations}
%\begin{itemize}
%\item {\bf International Society for Computational Biology} July 2012 - {\it (ongoing)}
%\end{itemize}


